SULI Report!

### 2015-08-17 doc/suli-report-swe.tex
Restructured the first two sentences of the introduction to better describe dark matter. #81

In a universe teeming with galaxies and light, it came as a shock to 20th century astronomers that most of the mass in the universe is in fact dark. The `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe, and only (4.9\%?) of the mass-energy content of the universe (cite L-CDM). While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).

>>>>

In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers unexpectedly discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe, while the rest takes the form of an exotic dark matter that does not absorb or emit light rendering it invisible to our telescopes. While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).
